On Optimality of Finite Element Integration

### 2015-10-29 TOMS_Paper/assembly.tex
A few small fixes

% Page heads
\markboth{F. Luporini et al.}{Optimality and Heuristics for Finite Element Integration}

% Title portion
\title{Optimality and Heuristics for Finite Element Integration}
\author{Fabio Luporini
\affil{Imperial College London}
David A. Ham
\affil{Imperial College London}
Paul H.J. Kelly
\affil{Imperial College London}}

@@

\acmformat{Fabio Luporini, David A. Ham, and Paul   H. J. Kelly, 2015. Optimality and Heuristics for Finite Element Integration.}

>>>>

% Page heads
\markboth{F. Luporini et al.}{On Optimality of Finite Element Integration}

% Title portion
\title{On Optimality of Finite Element Integration}
\author{Fabio Luporini
\affil{Imperial College London}
David A. Ham
\affil{Imperial College London}
Paul H. J. Kelly
\affil{Imperial College London}}

@@

\acmformat{Fabio Luporini, David A. Ham, and Paul H. J. Kelly, 2015. On Optimality of Finite Element Integration.}
